DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-19 ase2017/paper.tex

\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subfig} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{pgfplots}

@@

Instead of unfolding the dynamics, the second approach shown in Figure~\ref{fig:CEGARIS}
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
evaluate all possible progressions of the system simultaneously. 
Additionally, the second approach uses abstraction refinement,
enabling us to always start with a very simple description regardless of the
dynamics complexity, and only expand to more complex models
when a solution cannot be found.

\textcolor{red}{Dario: Can you please expand a bit further the second approach}

>>>>

\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{epstopdf} %converting to PDF
\usepackage{subfig} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{pgfplots}

@@

Instead of unfolding the dynamics, the second approach shown in Figure~\ref{fig:CEGARIS}
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
evaluate all possible progressions of the system simultaneously. This eliminates the need for
a completenes threshold since the time horizon is always infinite.
Since this model is based on abstraction, we initially perform the synthesis over a basic
model that abstracts away the complexity of the specification and is only refined to a more
complex model when a counterexample is found. Thus we may only look at the gain of the
system to synthesise a controller and add further restrictions on specific sections of the reach
tube when these prove to invalidate the solution. The use of Counter-Example Guided 
Abstraction Refinement results in much faster synthesis and verification since it is applied to
both phases,allowing for faster results whilst maintaining soundness for an infinite time horizon.
